---
title: "Assignment"
author: "Scott Stoltzman"
date: "6/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('tidyverse')
library('caret')

#install.packages(c('DMwR', 'ROSE'))
```


# Assignment  

You are on a crack squad of a group looking into whether or not reviews came from the USA. This field in your data set is `review_from_usa` and is either `TRUE` or `FALSE`. Use the data and a logistic regression model to predict whether or not the review is coming from the USA. Describe your process along the way and use best practices that you have learned so far.


## Before Starting:
Read about the data at <https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-06-04>

# Data Source

```{r}
ramen_ratings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-04/ramen_ratings.csv")
```

# Begin EDA 

```{r}
dat <- ramen_ratings %>%
  mutate(review_from_usa = country == 'United States') %>%
  select(-country, -review_number) %>% 
  rename(Class = review_from_usa) %>% 
  mutate(Class = as.factor(as.numeric(Class)))

head(dat)
```

```{r}
summary(dat)
```

```{r}
select(dat:variety)
```


# Expore NA values
Show how many `NA` there are and how to interpret these `NA` values, explain what you will do with them.
< Can delete the rows that contain NAs, or impute the continuous variables. I decided to just remove the rows. >
```{r}
#colSums(is.na(dat))
na_data <- dat %>%
  filter(!is.na(stars)) %>% 
  filter(!is.na(style))
#  mutate(stars = if_else(is.na(stars), mean(stars), stars))
```

# Create ID Column
```{r}
id_data <- na_data %>%
  mutate(id = row_number()) %>% 
  select(id, Class, everything())
```

```{r}
id_data %>% 
  group_by(Class) %>% 
  summarise(n=n())
```


# Look at data balance
```{r}
id_data %>%
  group_by(Class) %>%
  count() %>%
  ggplot(aes(x = Class, y = n)) +
  geom_col() + 
  geom_label(aes(label = scales::percent(n / sum(n))))
```

# Split data into Train and Test 80/20
```{r}
set.seed(123)

train_data <- id_data %>%
  sample_n(2530)

test_data <- id_data %>%
  anti_join(train_data, by = 'id')

train_data <- train_data %>% select(-id)
test_data <- test_data %>% select(-id)
```

# Look at Down Sample 
```{r}
down_train <- downSample(x = train_data[, -ncol(train_data)],
                         y = train_data$Class)
table(down_train$Class)
```

# Look at Up Sample 
```{r}
up_train <- upSample(x = train_data[, -ncol(train_data)],
                         y = train_data$Class)
table(up_train$Class)
```

# Look at Hybrid - SMOTE 
```{r}
# Requires a data.frame, not tibble
train_data_df <- as.data.frame(train_data)
smote_train <- DMwR::SMOTE(Class ~ ., data = train_data_df)
table(smote_train$Class)
```

# Look at Hybrid - ROSE 
```{r}
rose_train <- ROSE::ROSE(Class ~ ., data = train_data)$data
table(rose_train$Class) 
```


# K-Fold Parameters 
```{r}
# Parameters
train_control <- trainControl(method = "cv", number = 5)
```

# Model using up-sampling 
```{r}
model_data <- up_train

model <- train(model_data, Class ~ ., data = model_data, method = "glm", family = "binomial", trControl = train_control)

predictions <- predict(model, newdata = test_data, type = 'raw')
actuals <- test_data$Class
confusionMatrix(predictions, actuals)
```

# No sub-sampling 
```{r}
model_data <- train_data

model <- train(Class ~ ., data = model_data, method = "glm", family = "binomial", trControl = train_control)

predictions <- predict(model, newdata = test_data, type = 'raw')
actuals <- test_data$Class
confusionMatrix(predictions, actuals)
```

# Model using down sampling 
```{r}
model_data <- down_train

model <- train(Class ~ ., data = model_data, method = "glm", family = "binomial", trControl = train_control)

predictions <- predict(model, newdata = test_data, type = 'raw')
actuals <- test_data$Class
confusionMatrix(predictions, actuals)
```

# Model using SMOTE sampling 
```{r}
model_data <- smote_train

model <- train(Class ~ ., data = model_data, method = "glm", family = "binomial", trControl = train_control)

predictions <- predict(model, newdata = test_data, type = 'raw')
actuals <- test_data$Class
confusionMatrix(predictions, actuals)
```

# Model using ROSE sampling 
```{r}
model_data <- rose_train

model <- train(Class ~ ., data = data_to_use, method = "glm", family = "binomial", trControl = train_control)

predictions <- predict(model, newdata = test_data, type = 'raw')
actuals <- test_data$Class
confusionMatrix(predictions, actuals)
```



