---
title: "Assignment"
author: "Scott Stoltzman"
date: "6/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('tidyverse')
```


## Before Starting:
Read about the data at <https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-05-21>

```{r}
coast_vs_waste <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-21/coastal-population-vs-mismanaged-plastic.csv")

mismanaged_vs_gdp <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-21/per-capita-mismanaged-plastic-waste-vs-gdp-per-capita.csv")

waste_vs_gdp <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-21/per-capita-plastic-waste-vs-gdp-per-capita.csv")

```


# Begin EDA 
```{r}
# Clean Names - helps quite a bit!
coast_vs_waste = coast_vs_waste %>% janitor::clean_names()
mismanaged_vs_gdp = mismanaged_vs_gdp %>% janitor::clean_names()
waste_vs_gdp = waste_vs_gdp %>% janitor::clean_names()
```


# Expore NA values
Show how many `NA` there are and how to interpret these `NA` values
< Answer Here >
```{r}
coast_vs_waste
```

Are there any groups of data with `NA` that stand out? Why or why not?
< Answer Here >
```{r}
coast_vs_waste
```



Show how many `NA` there are and how to interpret these `NA` values
< Answer Here >
```{r}
mismanaged_vs_gdp
```

Are there any groups of data with `NA` that stand out? Why or why not?
< Answer Here >
```{r}
mismanaged_vs_gdp
```




Show how many `NA` there are and how to interpret these `NA` values
< Answer Here >
```{r}
waste_vs_gdp
```

Are there any groups of data with `NA` that stand out? Why or why not?
< Answer Here > 
```{r}
waste_vs_gdp
```



# Join data
If you performed a left join between `coast_vs_waste` and `mismanaged_vs_gdp`:
  - How would you join them? 
  
  <answer here>
  
  - How many rows and columns would you expect?
  
  < Answer Here >


What is wrong with the following `left_join`?
< Answer Here >
```{r}
coast_vs_waste %>% 
  left_join(mismanaged_vs_gdp, by = 'code')
```


Perform the left join:
```{r}
# coast_vs_waste LEFT JOIN mismanaged_vs_gdp ... use the tidyverse (not raw SQL)
```


In words, if you were writing tests in your code, how would you check its accuracy?
<Answer Here>


In code, check to ensure you still have all of the years for each country from the previously joined tables.
```{r}
# Here is an example to see if x equals y
frank = "FRANK"
chase = "CHASE"
assertthat::are_equal(frank, chase) #returns FALSE
# Create a similar test to see if each country still has all of the years
```

Join at least two of the data sets and create a linear regression with the `lm()` function. Make sure to use a group_by that makes sense and use 2 or more predictor variables.
```{r}
# left_join data
# then
# group_by _____
# lm() **Remember the do() function**
```

Display coefficients from your model.
```{r}
# write code to display them
```

Plot your data and add a line of what the model would predict. *Advanced topic*
```{r}
# ggplot()
```

From your analysis of the data, what would you propose as a policy decision to reduce waste? Be thorough, highlight data points that matter in tables and charts and supply succinct sentences. 
```{r}
# Kick it off here!
```

