---
title: "Assignment10"
author: "Frank Bonifazi"
date: "6/17/2019"
output: html_document
---

#```{r}
install.packages("tidyverse")
install.packages("janitor")
#```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("janitor")
```


## Before Starting:
Read about the data at <https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-05-21>

```{r}
coast_vs_waste <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-21/coastal-population-vs-mismanaged-plastic.csv")
```

```{r}
mismanaged_vs_gdp <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-21/per-capita-mismanaged-plastic-waste-vs-gdp-per-capita.csv")
```

```{r}
waste_vs_gdp <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-21/per-capita-plastic-waste-vs-gdp-per-capita.csv")

```


# Begin EDA 
```{r}
# Clean Names - helps quite a bit!
coast_vs_waste = coast_vs_waste %>% janitor::clean_names()
#FB: All lower-case with "_" underscores between words!

mismanaged_vs_gdp = mismanaged_vs_gdp %>% janitor::clean_names()

waste_vs_gdp = waste_vs_gdp %>% janitor::clean_names()
```
```{r}
coast_vs_waste %>%
  colnames()
```

# Explore NA values
Show how many `NA` there are and how to interpret these `NA` values



```{r}
coast_vs_waste %>%
  filter(is.na(entity)) #%>%
  #count()  FB: Why does count say 1???
# Zero NAs
```



```{r}
coast_vs_waste %>%
  filter(is.na(code))
  #FB: zero NAs
```

```{r}
coast_vs_waste %>%
  filter(is.na(year))
  #FB: zero NAs
```

```{r}
coast_vs_waste %>%
  filter(is.na(mismanaged_plastic_waste_tonnes)) %>%
 count()
#print(n)
#coast_vs_waste_NAs <- n
#print(n)
  #FB: 19,906 NAs
```


```{r}
coast_vs_waste %>%
  filter(is.na(coastal_population))
  #FB: 19,907 NAs
```
```{r}
coast_vs_waste %>%
  filter(is.na(total_population_gapminder))
  #FB: 12 NAs
```


< 39,825 > 
FB: Per data_frame?
Total # NAs in coast_vs.waste = 39,825


Are there any groups of data with `NA` that stand out? Why or why not?

```{r}
coast_vs_waste %>%
  select(mismanaged_plastic_waste_tonnes, total_population_gapminder) %>%
filter(is.na (mismanaged_plastic_waste_tonnes)) %>%
 filter(is.na (total_population_gapminder)) 
  
```
FB:
- Columns: mismanaged_plastic_waste_tonnes and total_population_gapminder don't have NAs in the same rows.

- The 12 NAs for total_population_gapminder are all for year  2010 and have a coastal_population (<= 6M), except a place named "World"/OWID_WRL which has a 0 coastal_population.  What could this be????




Show how many `NA` there are and how to interpret these `NA` values
< Answer Here >

```{r}
mismanaged_vs_gdp %>%
  colnames()
```

Are there any groups of data with `NA` that stand out? Why or why not?
< Answer Here >
```{r}
mismanaged_vs_gdp %>%
  filter(is.na(entity)) %>%
  count()

```
FB: Zero NAs


```{r}
mismanaged_vs_gdp %>%
  filter(is.na(code)) %>%
count()
```

FB: 1,240 NAs.  NOTE: Maybe there are codes for these countries in the other tables!

```{r}
mismanaged_vs_gdp %>%
  filter(is.na(year)) %>%
count()
```
FB: Zero NAs

```{r}
mismanaged_vs_gdp %>%
  filter(is.na(per_capita_mismanaged_plastic_waste_kilograms_per_person_per_day)) %>%
  count()
```
$FB: Wow 22,018 NAs.... could this be calculated from other vars???


```{r}
mismanaged_vs_gdp %>%
  filter(is.na(gdp_per_capita_ppp_constant_2011_international_rate)) %>%
  count()
```
#FB: 15,797 NAs.

```{r}
mismanaged_vs_gdp %>%
  filter(is.na(total_population_gapminder)) %>%
  count()
```
FB: 2,123 NAs.  Hoe does this compare with total_population_gapminder in dataset coast_vs.waste? That dataset only had 6 NAs.  Maybe I can fill in some NAs from that data?

Show how many `NA` there are and how to interpret these `NA` values

< Answer Here >


```{r}
waste_vs_gdp %>%
  colnames()
```

```{r}
waste_vs_gdp %>%
  filter(is.na(entity)) %>%
  count()
```


#FB: Zerop NAs

```{r}
waste_vs_gdp %>%
  filter(is.na(code)) %>%
  count()
```

#FB: There are 1,240 NAs in code....same number (could be different ones though) as in mismanaged_vs_gdp. Need to compare.

```{r}
waste_vs_gdp %>%
  filter(is.na(year)) %>%
  count()
```
#FB: Zero NAs

```{r}
waste_vs_gdp %>%
  filter(is.na(per_capita_plastic_waste_kilograms_per_person_per_day)) %>%
  count()
```

#FB: 22,018 NAs.

```{r}
waste_vs_gdp %>%
  filter(is.na(gdp_per_capita_ppp_constant_2011_international_constant_2011_international)) %>%   count()
```

#FB: 15,797 NAs.

```{r}
waste_vs_gdp %>%
  filter(is.na(total_population_gapminder)) %>%
  count()
```
#FB: 2,123 NAs

Are there any groups of data with `NA` that stand out? Why or why not?
< the "per_capita" numbers are high, but maybe we can compute them from the other data.The 1,240 code NAs is the same number as for the coast_vs.waste data, but might be a differnt set.> 

```{r}
waste_vs_gdp  #FB: What do you want me to do here????
```



# Join data
If you performed a left join between `coast_vs_waste` and `mismanaged_vs_gdp`:
  - How would you join them?
  <answer here: Start with coast_vs_waste and left join mismanaged_vs_gdp using column code >
  

  

  There are 4 common columns between these 2 datasets:

coast_vs_waste
[1] "entity"  <COMMON>                       
[2] "code"    <COMMON>                        
[3] "year"    <COMMON>                        
[4] "mismanaged_plastic_waste_tonnes"
[5] "coastal_population"             
[6] "total_population_gapminder"  <COMMON> 

mismanaged_vs_gdp
[1] "entity"  <COMMON>                                         
[2] "code"    <COMMON>                                          
[3] "year"    <COMMON>                                           
[4] "per_capita_mismanaged_plastic_waste_kilograms_per_person_per_day"
[5] "gdp_per_capita_ppp_constant_2011_international_rate"         
[6] "total_population_gapminder"  <COMMON>                    
  
  
  - How many rows and columns would you expect?
  
  < 8 with a left_join>


What is wrong with the following `left_join`?
< It's created 2M+ rows! And it's remaming several columns with var.x and var.y.>
```{r}
coast_vs_waste %>% 
  left_join(mismanaged_vs_gdp, by = 'code')
```


Perform the left join:
```{r}
# coast_vs_waste LEFT JOIN mismanaged_vs_gdp ... use the tidyverse (not raw SQL)
coast_vs_waste %>%
left_join(mismanaged_vs_gdp, by = c('code', 'entity', 'year'))


```
#FB: Same number of rows this time!

In words, if you were writing tests in your code, how would you check its accuracy?
<1 - make sure the number of resulting rows makes sense, and check is the colomn names have changed. Do some filters/queries before and after to check values.>


In code, check to ensure you still have all of the years for each country from the previously joined tables.


```{r}
# Here is an example to see if x equals y
frank = "FRANK"
chase = "CHASE"
assertthat::are_equal(frank, chase) #returns FALSE
# Create a similar test to see if each country still has all of the years
```
```{r}

  year_list1 <- coast_vs_waste
  year_list1 %>%
  select(entity, year)

```



```{r}
year_list2 <- coast_vs_waste
  year_list2 %>%
left_join(mismanaged_vs_gdp, by = c('entity', 'year')) %>%
     select(entity, year)
 assertthat::are_equal(year_list1, year_list2)
  
```
#FB: Same number of rows....How to compare these 2 results?

```{r}
#FB: Create a tempory tibble with just the years
coast_vs_waste_comp <- coast_vs_waste
coast_vs_waste_comp %>%
  select(year)

#FB: Create the joined result
coast_vs_waste_mis <- coast_vs_waste
   coast_vs_waste_mis %>%
   left_join(mismanaged_vs_gdp, by = 'code') %>%
   select(year.x)
   
   
#FB: Compare the 2 tibbles.
assertthat::are_equal(coast_vs_waste_comp, coast_vs_waste_mis )
```

  #FB The 2 tables are the same!



Join at least two of the data sets and create a linear regression with the `lm()` function. Make sure to use a group_by that makes sense and use 2 or more predictor variables.

```{r}
coast_vs_waste %>%

 select(entity, year, code, total_population_gapminder) %>%
 filter(code=="USA") %>%

  ggplot(aes(x=as.factor(year), y=total_population_gapminder)) +
  geom_point(title = "For USA")
  

```
#FB: This looks like a good candidate fir a linear model!

```{r}
# left_join data
# then
# group_by _____
coast_vs_waste %>%
  select(entity, year, code, total_population_gapminder) %>%
 filter(code=="USA") %>%
lm(total_population_gapminder ~ year, data = .) %>%
  summary
```

#FB: Statistically valid model - essentual 0 p-value.
R^2 is very high, so error is low.


#```{r}
coast_vs_waste %>%
lm() 
#```
Display coefficients from your model.
```{r}
# write code to display them


# left_join data
# then
# group_by _____
coast_vs_waste %>%
 select(entity, year, code, total_population_gapminder) %>%
 filter(code=="USA") %>%
summary() #%>%
#model1 <- lm(total_population_gapminder ~ year, data = .) #%>% #conf.level_tidy(model1, conf.level = 0.95, func = stats::confint)

```

Plot your data and add a line of what the model would predict. *Advanced topic*
```{r}
# ggplot()
```

From your analysis of the data, what would you propose as a policy decision to reduce waste? Be thorough, highlight data points that matter in tables and charts and supply succinct sentences. 
```{r}
# Kick it off here!
```

Kick!