---
title: "in_class"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('caret')
library('tidyverse')

# install.packages(c('DMwR', 'ROSE'))
```


Understanding Bias vs Variance
```{r}
set.seed(123)
raw_dat = ggplot2::diamonds
dat = raw_dat %>% sample_n(1000)

dat %>%
  ggplot(aes(x = carat, y = price)) +
  geom_point()
```

Bias vs Variance
```{r}
dat_to_split = dat %>%
  select(price, carat) %>%
  mutate(id = row_number())

dat_train = dat_to_split %>%
  sample_n(700)

dat_test = dat_to_split %>%
  anti_join(dat_train, by = 'id') %>%
  sample_n(300)


# linear fit
mod_lin = lm(price ~ carat, data = dat_train)  

# polynomial fit (10 degree)
mod_poly = lm(price ~ poly(carat, 10), data = dat_train)  
summary(mod_poly)
```

Predictions vs. training data set
```{r}
preds_lin_train = predict(mod_lin, newdata = dat_train)
preds_poly_train = predict(mod_poly, newdata = dat_train)

# add to a data set
dat_preds_train = dat_train %>% 
  mutate(preds_lin = preds_lin_train,
         preds_poly = preds_poly_train,
         carat = carat,
         price = price) %>%
  select(-id)

dat_preds_train %>%
  ggplot(aes(x = carat)) + 
  geom_point(aes(y = price)) + 
  geom_line(aes(y = preds_lin), col = 'red') + 
  geom_line(aes(y = preds_poly), col = 'blue')
```

Predictions vs Test Data Set
```{r}
preds_lin_test = predict(mod_lin, newdata = dat_test)
preds_poly_test = predict(mod_poly, newdata = dat_test)

# add to a data set
dat_preds_test = dat_test %>% 
  mutate(preds_lin = preds_lin_test,
         preds_poly = preds_poly_test,
         carat = carat,
         price = price) %>%
  select(-id)

dat_preds_test %>%
  ggplot(aes(x = carat)) + 
  geom_point(aes(y = price)) + 
  geom_line(aes(y = preds_lin), col = 'red') + 
  geom_line(aes(y = preds_poly), col = 'blue')
```




```{r}
dat_preds_test_tbl = tibble(price = integer(), preds_lin = double(), preds_poly = double(), model = integer())
dat_mse_tbl = tibble(mse_lin = double(), mse_poly_5 = double(), mse_poly_10 = double(), model = integer())
for(i in 1:20){
  dat_to_split = dat %>%
    select(price, carat) %>%
    mutate(id = row_number())
  dat_train = dat_to_split %>%
    sample_n(700)
  dat_test = dat_to_split %>%
    anti_join(dat_train, by = 'id') %>%
    sample_n(300)
  # linear fit
  mod_lin = lm(price ~ carat, data = dat_train)  
  # polynomial fit (5 degree)
  mod_poly_5 = lm(price ~ poly(carat, 5), data = dat_train)
  # polynomial fit (10 degree)
  mod_poly_10 = lm(price ~ poly(carat, 10), data = dat_train)
  
  preds_lin_test = predict(mod_lin, newdata = dat_test)
  preds_poly_5_test = predict(mod_poly_5, newdata = dat_test)
  preds_poly_10_test = predict(mod_poly_10, newdata = dat_test)
  
  # add to a data set
  dat_preds_test = dat_test %>% 
    mutate(preds_lin = preds_lin_test,
           preds_poly_5 = preds_poly_5_test,
           preds_poly_10 = preds_poly_10_test,
           carat = carat,
           price = price,
           residuals_lin = preds_lin - price,
           residuals_poly_5 = preds_poly_5 - price,
           residuals_poly_10 = preds_poly_10 - price,
           model = i) %>%
    select(-id)
  
  dat_preds_test_tbl = bind_rows(dat_preds_test_tbl, dat_preds_test)
  
  dat_mse = tibble(mse_lin = mean(mod_lin$residuals^2), 
                   mse_poly_5 = mean(mod_poly_5$residuals^2), 
                   mse_poly_10 = mean(mod_poly_10$residuals^2), 
                   model = i)
  dat_mse_tbl = bind_rows(dat_mse_tbl, dat_mse)
  
}

dat_preds_test_tbl %>%
  ggplot(aes(x = carat, group = model)) + 
  geom_point(aes(y = price)) + 
  geom_line(aes(y = preds_lin), col = 'red', alpha = 0.5) + 
  geom_line(aes(y = preds_poly_5), col = 'blue', alpha = 0.5) + 
  geom_line(aes(y = preds_poly_10), col = 'green', alpha = 0.5)

```


```{r}
dat_preds_test_tbl %>%
  filter(abs(preds_poly_10) < 20000) %>%
  ggplot(aes(x = carat, group = model)) + 
  geom_point(aes(y = price)) + 
  geom_line(aes(y = preds_lin), col = 'red', alpha = 0.5) + 
  geom_line(aes(y = preds_poly_5), col = 'blue', alpha = 0.5) + 
  geom_line(aes(y = preds_poly_10), col = 'green', alpha = 0.5)
```


Training Error
```{r}
dat_mse_tbl %>%
  ggplot() +
  geom_density(aes(mse_lin), fill = 'red', alpha = 0.5) +
  geom_density(aes(mse_poly_5), fill = 'blue', alpha = 0.5) +
  geom_density(aes(mse_poly_10), fill = 'green', alpha = 0.5)
```


Test Error
```{r}
dat_preds_test_tbl %>%
  group_by(model) %>%
  summarize(mse_lin = mean(residuals_lin^2),
            mse_poly_5 = mean(residuals_poly_5^2),
            mse_poly_10 = mean(residuals_poly_10^2)) %>%
  filter(mse_poly_10 < 2e9) %>%
  ggplot() + 
  geom_density(aes(mse_lin), fill = 'red', alpha = 0.5) +
  geom_density(aes(mse_poly_5), fill = 'blue', alpha = 0.5) +
  geom_density(aes(mse_poly_10), fill = 'green', alpha = 0.5)
```


```{r}
dat_preds_test_tbl %>%
  group_by(model) %>%
  summarize(mse_lin = mean(residuals_lin^2),
            mse_poly_5 = mean(residuals_poly_5^2),
            mse_poly_10 = mean(residuals_poly_10^2)) %>%
  filter(mse_poly_10 < 5e6) %>%
  ggplot() + 
  geom_density(aes(mse_lin), fill = 'red', alpha = 0.5) +
  geom_density(aes(mse_poly_5), fill = 'blue', alpha = 0.5) +
  geom_density(aes(mse_poly_10), fill = 'green', alpha = 0.5)
```





Moving to Cross Validation
```{r}
# Parameters
train_control = trainControl(
    method = "cv", number = 5,
    verboseIter = TRUE
  )

# K-fold (5 fold)
model_k_5 = train(
  price ~ carat, 
  data = dat_train,
  method = "lm",
  trControl = train_control
)
```

```{r}
summary(model_k_5)
```


```{r}
dat  = as_tibble(ISLR::Default)
dat
```


Let's revisit the Default data set. "Yes" is a much smaller portion of the data. This imbalance will make it really difficult to predict this class. We would like to get an even balance of data in this case.
```{r}
dat %>%
  group_by(default) %>%
  count() %>%
  ggplot(aes(x = default, y = n)) +
  geom_col() + 
  geom_label(aes(label = scales::percent(n / sum(n))))
```


Sampling Techniques
```{r}
dat_id = dat %>%
  mutate(id = row_number(),
         default = as.factor(default))

dat_train = dat_id %>%
  sample_n(7000)

dat_test = dat_id %>%
  anti_join(dat_train, by = 'id')

# would remove id if using to train, keeping it for an example.
```

Downsample
```{r}
down_train <- downSample(x = dat_train[, -ncol(dat_train)],
                         y = dat_train$default)
table(down_train$default)  
```

Upsample
```{r}
up_train <- upSample(x = dat_train[, -ncol(dat_train)],
                         y = dat_train$default)
table(up_train$default)   
```

Hybrid - SMOTE
```{r}
# Requires a data.frame, not tibble
dat_train_df = as.data.frame(dat_train)
smote_train <- DMwR::SMOTE(default ~ ., data = dat_train_df)
table(smote_train$default)   
```


Hybrid - ROSE
```{r}
rose_train <- ROSE::ROSE(default ~ ., data = dat_train)$data
table(rose_train$default)   
```




Training...
```{r}
# caret has a stronge thing... must have "Class" as the predicted variable
dat_test = dat_test %>% rename(Class = default) %>% mutate(Class = as.factor(Class))
dat_train = dat_train %>% rename(Class = default) %>% mutate(Class = as.factor(Class))
down_train = down_train %>% select(-default) #rename(Class = default) %>% mutate(Class = as.factor(Class)) huh?
up_train = up_train %>% select(-default) #rename(Class = default) %>% mutate(Class = as.factor(Class)) huh?
smote_train = smote_train %>% rename(Class = default) %>% mutate(Class = as.factor(Class))
rose_train = rose_train %>% rename(Class = default) %>% mutate(Class = as.factor(Class))


# Parameters
train_control = trainControl(
    method = "cv", number = 5
  )
```



No sub sampling
```{r}
data_to_use = dat_train %>% select(-id)

model = train(
  Class ~ ., 
  data = data_to_use,
  method = "glm",
  family = "binomial",
  trControl = train_control
)


predictions = predict(model, newdata = dat_test, type = 'raw')
actuals = dat_test$Class
confusionMatrix(predictions, actuals)
```


Downsampling
```{r}
data_to_use = down_train # %>% select(-id)

model = train(
  Class ~ ., 
  data = data_to_use,
  method = "glm",
  family = "binomial",
  trControl = train_control
)


predictions = predict(model, newdata = dat_test, type = 'raw')
actuals = dat_test$Class
confusionMatrix(predictions, actuals)
```


Upsampling
```{r}
data_to_use = up_train # %>% select(-id)

model = train(
  Class ~ ., 
  data = data_to_use,
  method = "glm",
  family = "binomial",
  trControl = train_control
)


predictions = predict(model, newdata = dat_test, type = 'raw')
actuals = dat_test$Class
confusionMatrix(predictions, actuals)
```

SMOTE
```{r}
data_to_use = smote_train %>% select(-id)

model = train(
  Class ~ ., 
  data = data_to_use,
  method = "glm",
  family = "binomial",
  trControl = train_control
)


predictions = predict(model, newdata = dat_test, type = 'raw')
actuals = dat_test$Class
confusionMatrix(predictions, actuals)
```


ROSE
```{r}
data_to_use = rose_train %>% select(-id)

model = train(
  Class ~ ., 
  data = data_to_use,
  method = "glm",
  family = "binomial",
  trControl = train_control
)


predictions = predict(model, newdata = dat_test, type = 'raw')
actuals = dat_test$Class
confusionMatrix(predictions, actuals)
```